---
title: "HOPE Analysis - For Klaus"
author: "Chloé Winters"
date: "2026-09-05"

output:
  word_document:
    toc: yes
    toc_depth: '4'
  html_document:           # output document format
    toc: yes               # add table contents
    toc_float: yes         # toc_property: floating
    toc_depth: 4           # depth of TOC headings
    fig_width: 6           # global figure width
    fig_height: 4          # global figure height
    fig_caption: yes       # add figure caption
    number_sections: yes   # numbering section headings
    toc_collapsed: yes     # TOC subheading clapsing
    code_folding: hide     # folding/showing code 
    code_download: yes     # allow to download complete RMarkdown source code
    smooth_scroll: yes     # scrolling text of the document
    theme: lumen           # visual theme for HTML document only
    highlight: tango       # code syntax hightlighting styles
  pdf_document: 
    toc: yes
    toc_depth: 4
    fig_caption: yes
    number_sections: yes
---

```{css, echo = FALSE}
div#TOC li {     /* table of content  */
    list-style-type: disc;;
    background-image:none;
    background-repeat:none;
    background-position:0;
}

h1.title {    /* level 1 header of title  */
  font-size: 24px;
  font-weight: bold;
  color: DarkRed;
  text-align: center;
}

h4.author { /* Header 4 - and the author and data headers use this too  */
  font-size: 18px;
  font-weight: bold;
  font-family: "Times New Roman", Times, serif;
  color: DarkRed;
  text-align: center;
}

h4.date { /* Header 4 - and the author and data headers use this too  */
  font-size: 18px;
  font-weight: bold;
  font-family: "Times New Roman", Times, serif;
  color: DarkBlue;
  text-align: center;
}

h1 { /* Header 1 - and the author and data headers use this too  */
    font-size: 20px;
    font-weight: bold;
    font-family: "Times New Roman", Times, serif;
    color: darkred;
    text-align: center;
}

h2 { /* Header 2 - and the author and data headers use this too  */
    font-size: 18px;
    font-weight: bold;
    font-family: "Times New Roman", Times, serif;
    color: navy;
    text-align: left;
}

h3 { /* Header 3 - and the author and data headers use this too  */
    font-size: 16px;
    font-weight: bold;
    font-family: "Times New Roman", Times, serif;
    color: navy;
    text-align: left;
}

h4 { /* Header 4 - and the author and data headers use this too  */
    font-size: 14px;
  font-weight: bold;
    font-family: "Times New Roman", Times, serif;
    color: darkred;
    text-align: left;
}

/* Add dots after numbered headers */
.header-section-number::after {
  content: ".";
}
```




```{r setup, include=FALSE}
# code chunk specifies whether the R code, warnings, and output 
# will be included in the output files.
library(knitr)
knitr::opts_chunk$set(echo = TRUE,           # include code chunk in the output file
                      warning = FALSE,       # sometimes, you code may produce warning messages,
                                              # you can choose to include the warning messages in
                                              # the output file. 
                      results = TRUE          # you can also decide whether to include the output
                                              # in the output file.
                      )   



library(knitr)
library(pander)
library(mlbench)
library(dplyr)
library(readr)
library(stringr)
library(purrr)
library(ggcorrplot)
library(GGally)
library(ggplot2)
library(tidyr)
library(gridExtra)
library(vcd)
library(lubridate)
library(tidyverse)
library(car)
library(caret)
library(MASS)
library(pscl)
library(ggplot2)
library(pROC)
library(knitr)
library(pander)
library(mlbench)
library(MASS)
library(pROC)
library(readxl)
library(vcdExtra)

knitr::opts_chunk$set(echo = TRUE,      
                      warning = FALSE,   
                      messages = FALSE,  
                      results = TRUE,
                      comment = NA
                      )   

```


```{r}

HOPE <- read_excel("HOPE data 2024 SBNS_dataset_West Chester University_2025-02-20.xlsx")
 
```


# Question 72

Please indicate whether you have heard of or used any of the following campus-based resources. (Please select one response for each item.) 

o	Q72_X. Category    
o	1 = Have not heard of   
o	2 = Heard of it but have not used   
o	3 = Used   

## Emergency Grants

```{r}
# Remove missing/invalid responses
Q72_1_data <- HOPE[
  !is.na(HOPE$Q72_1) &
  !HOPE$Q72_1 %in% c(-99, 99) &
  !is.na(HOPE$LGBTQIA),
]

# Counts
table(Q72_1_data$Q72_1, Q72_1_data$LGBTQIA)

# Proportions within LGBTQIA groups
round(
  prop.table(
    table(Q72_1_data$Q72_1, Q72_1_data$LGBTQIA),
    margin = 2
  ),
  3
)

# Chi-square test
chisq.test(
  table(Q72_1_data$Q72_1, Q72_1_data$LGBTQIA)
)

```

In terms of the following question asked below

Please indicate whether you have heard of or used any of the following campus-based resources. (Please select one response for each item.)     

o	Q72_1. Emergency Grants    
o	1 = Have not heard of   
o	2 = Heard of it but have not used   
o	3 = Used  

There is not a statistical significant in proportionally how Cishet
students answered the question compared to how Queer students answered
the question.

## Campus Food Pantry

```{r}
# Remove missing/invalid responses
Q72_2_data <- HOPE[
  !is.na(HOPE$Q72_2) &
  !HOPE$Q72_2 %in% c(-99, 99) &
  !is.na(HOPE$LGBTQIA),
]

# Counts
table(Q72_2_data$Q72_2, Q72_2_data$LGBTQIA)

# Proportions within LGBTQIA groups
round(
  prop.table(
    table(Q72_2_data$Q72_2, Q72_2_data$LGBTQIA),
    margin = 2
  ),
  3
)

# Chi-square test
chisq.test(
  table(Q72_2_data$Q72_2, Q72_2_data$LGBTQIA)
)

```

In terms of the following question asked below

Please indicate whether you have heard of or used any of the following
campus-based resources. (Please select one response for each item.). 

o	Q72_2. Campus Food Pantry    
o	1 = Have not heard of   
o	2 = Heard of it but have not used   
o	3 = Used  

There is a statistical significant in proportionally how Cishet students
answered the question compared to how Queer students answered the
question. Looking at the proportion table, a larger proportion of Cishet
students had not heard of the Campus Food Pantry compared to Queer
students, with 23.4% of Cishet students being unaware of the food pantry
compared to 11.4% of Queer students. Additionally, proportionally less
Cishet students used the food pantry in comparison to queer students
with 10.2% of Cishet students using the food pantry compared to 19.5% of
Queer students using the food pantry.

## Food Stamps/SNAP

```{r}
# Remove missing/invalid responses
Q72_3_data <- HOPE[
  !is.na(HOPE$Q72_3) &
  !HOPE$Q72_3 %in% c(-99, 99) &
  !is.na(HOPE$LGBTQIA),
]

# Counts
table(Q72_3_data$Q72_3, Q72_3_data$LGBTQIA)

# Proportions within LGBTQIA groups
round(
  prop.table(
    table(Q72_3_data$Q72_3, Q72_3_data$LGBTQIA),
    margin = 2
  ),
  3
)

# Chi-square test
chisq.test(
  table(Q72_3_data$Q72_3, Q72_3_data$LGBTQIA)
)

```

In terms of the following question asked below

Please indicate whether you have heard of or used any of the following
campus-based resources. (Please select one response for each item.)  

o	Q72_3. Help Obtaining Food Stamps/SNAP    
o	1 = Have not heard of   
o	2 = Heard of it but have not used   
o	3 = Used  

There is a statistical significant in proportionally how Cishet students
answered the question compared to how Queer students answered the
question. Looking at the proportion table, a larger proportion of Cishet
students had not heard of help obtaining food stamps/SNAP compared to
Queer students, with 37.7% of Cishet students being unaware of the food
pantry compared to 27.6% of Queer students. Additionally, proportionally
less Cishet students had heard of but not used help obtaining food
stamps/SNAP in comparison to queer students with 57.1% of Cishet
students having heard of but not used help obtaining food stamps/SNAP to
67.2% of Queer students.

## Unemployment Benefits, WIC, TANF, etc.

```{r}
# Remove missing/invalid responses
Q72_4_data <- HOPE[
  !is.na(HOPE$Q72_4) &
  !HOPE$Q72_4 %in% c(-99, 99) &
  !is.na(HOPE$LGBTQIA),
]

# Counts
table(Q72_4_data$Q72_4, Q72_4_data$LGBTQIA)

# Proportions within LGBTQIA groups
round(
  prop.table(
    table(Q72_4_data$Q72_4, Q72_4_data$LGBTQIA),
    margin = 2
  ),
  3
)

# Chi-square test
chisq.test(
  table(Q72_4_data$Q72_4, Q72_4_data$LGBTQIA)
)

```

In terms of the following question asked below

Please indicate whether you have heard of or used any of the following
campus-based resources. (Please select one response for each item.). 

o	Q72_4. Help Applying For Other Public Supports, Such As Unemplyment Benefits, WIC, TANF, etc.     
o	1 = Have not heard of   
o	2 = Heard of it but have not used   
o	3 = Used  

There is not a statistical significant in proportionally how Cishet
students answered the question compared to how Queer students answered
the question.

## Food Scholarships, Meal Vouchers, or Another Source of Free Food

```{r}
# Remove missing/invalid responses
Q72_5_data <- HOPE[
  !is.na(HOPE$Q72_5) &
  !HOPE$Q72_5 %in% c(-99, 99) &
  !is.na(HOPE$LGBTQIA),
]

# Counts
table(Q72_5_data$Q72_5, Q72_5_data$LGBTQIA)

# Proportions within LGBTQIA groups
round(
  prop.table(
    table(Q72_5_data$Q72_5, Q72_5_data$LGBTQIA),
    margin = 2
  ),
  3
)

# Chi-square test
chisq.test(
  table(Q72_5_data$Q72_5, Q72_5_data$LGBTQIA)
)

```
In terms of the following question asked below

Please indicate whether you have heard of or used any of the following
campus-based resources. (Please select one response for each item.)   

o	Q72_5. Food Scholarships, Meal Vouchers, or Another Source of Free Food    
o	1 = Have not heard of   
o	2 = Heard of it but have not used   
o	3 = Used  

There is not a statistical significant in proportionally how Cishet
students answered the question compared to how Queer students answered
the question.

## Emergency Housing

```{r}
# Remove missing/invalid responses
Q72_6_data <- HOPE[
  !is.na(HOPE$Q72_6) &
  !HOPE$Q72_6 %in% c(-99, 99) &
  !is.na(HOPE$LGBTQIA),
]

# Counts
table(Q72_6_data$Q72_6, Q72_6_data$LGBTQIA)

# Proportions within LGBTQIA groups
round(
  prop.table(
    table(Q72_6_data$Q72_6, Q72_6_data$LGBTQIA),
    margin = 2
  ),
  3
)

# Chi-square test
chisq.test(
  table(Q72_6_data$Q72_6, Q72_6_data$LGBTQIA)
)

```

In terms of the following question asked below

Please indicate whether you have heard of or used any of the following
campus-based resources. (Please select one response for each item.)   

o	Q72_6. Emergency Housing    
o	1 = Have not heard of   
o	2 = Heard of it but have not used   
o	3 = Used  

There is a statistical significant in proportionally how Cishet students
answered the question compared to how Queer students answered the
question. Looking at the proportion table, a larger proportion of Cishet
students had not heard of emergency housing compared to Queer students, with 60.4% of Cishet students being unaware of emergency housing compared to 50.6% of Queer students. Additionally, proportionally less Cishet students had heard of but not used emergency housing in comparison to queer students with 39.3% of Cishet students having heard of but not used emergency housing compared to 48.2% of Queer students. Finally, less Cishet students had used emergency housing compared to Queer students, with 0.3% of Cishet students using emergency housing compared to 1.2% of queer students using emergency housing. 

## Help Finding Affordable Housing

```{r}
# Remove missing/invalid responses
Q72_7_data <- HOPE[
  !is.na(HOPE$Q72_7) &
  !HOPE$Q72_7 %in% c(-99, 99) &
  !is.na(HOPE$LGBTQIA),
]

# Counts
table(Q72_7_data$Q72_7, Q72_7_data$LGBTQIA)

# Proportions within LGBTQIA groups
round(
  prop.table(
    table(Q72_7_data$Q72_7, Q72_7_data$LGBTQIA),
    margin = 2
  ),
  3
)

# Chi-square test
chisq.test(
  table(Q72_7_data$Q72_7, Q72_7_data$LGBTQIA)
)

```

In terms of the following question asked below

Please indicate whether you have heard of or used any of the following
campus-based resources. (Please select one response for each item.).

o	Q72_7. Help Finding Affordable Housing    
o	1 = Have not heard of   
o	2 = Heard of it but have not used   
o	3 = Used  

There is not a statistical significant in proportionally how Cishet
students answered the question compared to how Queer students answered
the question.

## Transportation Resources, Such As A Bus Pass

```{r}
# Remove missing/invalid responses
Q72_8_data <- HOPE[
  !is.na(HOPE$Q72_8) &
  !HOPE$Q72_8 %in% c(-99, 99) &
  !is.na(HOPE$LGBTQIA),
]

# Counts
table(Q72_8_data$Q72_8, Q72_8_data$LGBTQIA)

# Proportions within LGBTQIA groups
round(
  prop.table(
    table(Q72_8_data$Q72_8, Q72_8_data$LGBTQIA),
    margin = 2
  ),
  3
)

# Chi-square test
chisq.test(
  table(Q72_8_data$Q72_8, Q72_8_data$LGBTQIA)
)

```

In terms of the following question asked below

Please indicate whether you have heard of or used any of the following
campus-based resources. (Please select one response for each item.). 

o	Q72_8. Transportation Resources, Such as a Bus Pass    
o	1 = Have not heard of   
o	2 = Heard of it but have not used   
o	3 = Used  

There is not a statistical significant in proportionally how Cishet
students answered the question compared to how Queer students answered
the question.

## A Campus Health Clinic and/or Counseling

```{r}
# Remove missing/invalid responses
Q72_9_data <- HOPE[
  !is.na(HOPE$Q72_9) &
  !HOPE$Q72_9 %in% c(-99, 99) &
  !is.na(HOPE$LGBTQIA),
]

# Counts
table(Q72_9_data$Q72_9, Q72_9_data$LGBTQIA)

# Proportions within LGBTQIA groups
round(
  prop.table(
    table(Q72_9_data$Q72_9, Q72_9_data$LGBTQIA),
    margin = 2
  ),
  3
)

# Chi-square test
chisq.test(
  table(Q72_9_data$Q72_9, Q72_9_data$LGBTQIA)
)

```

In terms of the following question asked below

Please indicate whether you have heard of or used any of the following
campus-based resources. (Please select one response for each item.). 

o	Q72_9. A Campus Health Clinic and/or Counseling    
o	1 = Have not heard of   
o	2 = Heard of it but have not used   
o	3 = Used  

There is a statistical significant in proportionally how Cishet studentsanswered the question compared to how Queer students answered the question. Looking at the proportion table, a larger proportion of Cishet students had not heard of a campus health clinic and/or counseling to Queer students, with 16.1% of Cishet students being unaware of a campus health clinic and/or counselingg compared to 8.2% of Queer students. Additonally, less Cishet students had used a campus health clinic and/or counseling compared to Queer students, with 16.8% of Cishet students using a campus health clinic and/or counseling compared to 26.2% of queer students using a campus health clinic and/or counseling. 

## Loaned or Free Wi-Fi Hotspot or Laptop

```{r}
# Remove missing/invalid responses
Q72_10_data <- HOPE[
  !is.na(HOPE$Q72_10) &
  !HOPE$Q72_10 %in% c(-99, 99) &
  !is.na(HOPE$LGBTQIA),
]

# Counts
table(Q72_10_data$Q72_10, Q72_10_data$LGBTQIA)

# Proportions within LGBTQIA groups
round(
  prop.table(
    table(Q72_10_data$Q72_10, Q72_10_data$LGBTQIA),
    margin = 2
  ),
  3
)

# Chi-square test
chisq.test(
  table(Q72_10_data$Q72_10, Q72_10_data$LGBTQIA)
)

```
In terms of the following question asked below

Please indicate whether you have heard of or used any of the following
campus-based resources. (Please select one response for each item.). 

o	Q72_10. Loaned or Free Wi-Fi Hotspot or Laptop    
o	1 = Have not heard of   
o	2 = Heard of it but have not used   
o	3 = Used  

There is not a statistical significant in proportionally how Cishet
students answered the question compared to how Queer students answered
the question.